Instructions for \confname{} Proceedings

### 2019-05-07 papers/EMNLP2019/analysis.tex

%
% File emnlp2019.tex
%
%% Based on the style files for ACL 2019, which were
%% Based on the style files for EMNLP 2018, which were
%% Based on the style files for ACL 2018, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp-ijcnlp-2019}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}  %%% for including graphics
\usepackage{booktabs}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP-IJCNLP 2019}
\newcommand\conforg{SIGDAT}

\title{Instructions for \confname{} Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
\end{abstract}

\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\vgenome}{VisualGenome\xspace}
\newcommand{\ra}{$\rightarrow$}

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}

\section{Introduction}

Expressions describing or referring to objects in visual scenes typically include a word naming the type of the object: e.g.,  \emph{cheesecake} or  \emph{dessert}  in Figure~\ref{fig:ex1}. 
Determining these objects names is a core aspect of virtually every language \& vision task, ranging from e.g.\ referring expression generation to visual dialogue.
Nevertheless, research in language \& vision has mostly  sidestepped questions about how speakers actually choose these names and how computational models should account for it.

While state-of-the-art computer vision systems are able to accurately classify images into thousands of different categories (e.g.\  \newcite{googlenet}), they mostly adopt very simple assumptions with respect to the underlying lexicon, which is typically implemented as a simple, flat labeling scheme. Thus, a standard object recognition system would be trained to classify the objects in Figure~\ref{fig:cake} as either  \emph{dessert} or \emph{cake}.
In contrast, humans seem to be more flexible as to the chosen level of generality and to the chosen part of the taxonomy (see objects in Figure \ref{fig:cake} that could be named \refexp{cake}, \refexp{cheesecake}, \refexp{dessert}, \refexp{sweet}, \refexp{pastry}, \refexp{food} etc.) 
Seminal work on prototypes suggests that the prototypicality of the object will determine the level of generality of the object name, i.e.\  a robin can be named \emph{bird}, but a penguin is better referred to as ``\emph{penguin}'' \cite{Rosch1978}.

%To date, surprisingly little work has been done on testing such theoretical predictions on large-scale, language \& vision data sets and integrating them explicitly into modeling frameworks.

\begin{figure}[htbp]
\begin{center}
\includegraphics[height=3cm]{Figures/cheescake.png}
\includegraphics[height=3cm]{Figures/cheesecak2.pdf}
\caption{Two objects of the same type of cake, with different names in VisualGenome}
\label{fig:cake}
\end{center}
\end{figure}

Two main findings in the literature:

\begin{itemize}
\item very high agreement, most people use the same name for the same object
\item prototypicality is a factor, context too, but research has only looked at generality/specificity of the name
\end{itemize}

\sz{something is missing here .. explain why exactly we did what we did, why is it interesting to collect many names for the same object?}

There are two main findings:

\begin{itemize}
\item the level of agreement in object naming is much higher in certain domains than in others, as it happens, the domains that have been traditionally used in object naming research (e.g. animals) seem to display the highest amount of agreement in our data set 
\item while previous work has mostly focussed on variation in the level of generality (\emph{penguin} vs. \emph{bird}), our datasets contains a lot of variability for names coming from different parts of the taxonomy (\emph{dessert} vs. \emph{cake}, \emph{bottle} vs. \emph{wine})
\end{itemize}

%The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories. And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy. For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc. Hence, when speakers name objects, e.g.\ when referring, they have to select a lexical item from a complex network of concepts and competing lexical alternatives.

%To date, research in NLP has surprisingly little to say about object naming, despite the fact that
% there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}. 
%In contrast, closely related areas, such as computer vision and cognitive science, have investigated very related tasks in quite some depth: object recognition systems developed in the area of computer vision  are now able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}).
%Furthermore, work on concepts, following the seminal work by Rosch, suggests that objects are typically conceptualized at a preferred level of specificity called the \textbf{entry-level}. Psycho-linguistic studies have been able to support this theory based on collections of so-called object naming norms. 
%
%This paper aims at addressing the genuinely linguistic questions revolving around the phenomenon of object naming by (i) presenting a collection of high-quality, large-scale naming data,  and (ii) analysis methods for this data and (iii) a first baseline model that accounts for the semantic flexibility of names for objects in real-world images. From computer vision, we borrow the idea of modeling realistic visual objects in realistic scenes (real-world images), but go beyond the simplistic assumption that object names correspond to unambiguous labels in a flat classification scheme (with no conceptual relations between the labels). From psycholinguistics, we borrow the idea of eliciting natural, representative naming data from many subjects, but go beyond using artificial, highly stylized objects.

\section{Related Work}

\section{Analysis}

@@

\begin{itemize}
\item \textbf{top \%}: for each object, we calculate the relative frequency of the most common name, and then average over all objects
\item \textbf{SD \%}: for each object, we calculate the Snodgrass agreement measure, and then average over all objects
\item \textbf{=VG}: the proportion of objects where the most frequent name coincides with the name annotated in VisualGenome
\end{itemize}

\begin{table*}
\small
\begin{tabular}{llll|llll|llll}
\toprule
    & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
                         domain & \% top &    SD &   =VG &         id &     \% top &    SD &   =VG &             id &     \% top &    SD &   =VG \\
\midrule
         people &  0.52 &  2.13 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.36 &  2.62 &  0.37 \\
       clothing &  0.64 &  1.58 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
           home &  0.66 &  1.50 &  0.78 &          tool.n.01 &  0.86 &  0.73 &  0.94 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
      buildings &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
           food &  0.71 &  1.30 &  0.63 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.53 &  1.97 &  0.15 \\
       vehicles &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.42 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
 animals,plants &  0.91 &  0.44 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
\bottomrule
 all &  0.70 &  1.34 &  0.73            \\

@@

Why is naming more flexible in certain domains than in others?

@@

In this section, we take a closer look at the lexical variation we observe in our data set. We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain. \sz{domains need to be updated}

@@

\begin{table}
\small
\begin{tabular}{llll}
\toprule
        relation & \% types & \% tokens & av. depth \\
\midrule
 co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
    hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
        synonymy &  0.015 &  0.121 &       1.000 \\
\bottomrule
\end{tabular}
\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?}}
\label{tab:rel}
\end{table}

@@

\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.}

@@

\subsection{Issues with WordNet}

@@

\begin{itemize}
\item lettuce -- salad
\item fruit -- food
\item man -- catcher
\item bowl --chili
\item bowl -- diner
\item burger -- meat
\item statue -- animal (image shows statue of an animal)
\item bottle -- alcohol
\item donut --desert
\item zebra -- stripes
\item oven -- grill
\end{itemize}

@@

\subsection{Entry-level names and preference orders....}

\sz{an interesting example:} In our data set, there are 24 images where \textit{penguin} has been used, so we know that the object is a \textit{penguin}. For 50\% of these images, annotators still prefer \textit{bird} as the most common name. According to the theory of entry-level categories, this should not happen. People should always prefer \textit{penguin} over \textit{bird}.

\sz{how can we analyze this quantitatively?}

@@

\subsection{Co-hyponyms as names for objects}

\sz{analyze and discuss why we find so many co-hyponyms in our data set}

\section{Modeling}

\sz{I think, the prevalence of co-hyponymy is the most interesting finding. Can we learn to predict whether to co-hyponyms can be used to name the same object?}

\end{document}

>>>>

@@

\begin{itemize}
\item \textbf{\% top}: for each object, we calculate the relative frequency of the most common name, and then average over all objects
\item \textbf{SN}: for each object, we calculate the Snodgrass agreement measure, and then average over all objects \gbt{Note: changing SD to SN cause SD is typically standard deviation}
\item \textbf{=VG}: the proportion of objects where the most frequent name coincides with the name annotated in VisualGenome
\end{itemize}

\begin{table*}
\small
\begin{tabular}{llll|llll|llll}
\toprule
    & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
                         domain & \% top &    SN &   =VG &         id &     \% top &    SN &   =VG &             id &     \% top &    SN &   =VG \\
\midrule
         people &  0.52 &  2.13 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.36 &  2.62 &  0.37 \\
       clothing &  0.64 &  1.58 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
           home &  0.66 &  1.50 &  0.78 &          tool.n.01 &  0.86 &  0.73 &  0.94 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
      buildings &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
           food &  0.71 &  1.30 &  0.63 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.53 &  1.97 &  0.15 \\
       vehicles &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.42 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
 animals,plants &  0.91 &  0.44 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
\bottomrule
 all &  0.70 &  1.34 &  0.73            \\

@@

Why is naming more flexible in certain domains than in others? \gbt{Hypothesis: expectation: little variation - hypernymy at most, more variation <-> more affordances <-> more varied relationships.}

@@

In this section, we take a closer look at the lexical variation we observe in our data set. We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain.

@@

\begin{table}
\small
\begin{tabular}{llll}
\toprule
        relation & \% types & \% tokens & av. depth \\
\midrule
 co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
    hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
        synonymy &  0.015 &  0.121 &       1.000 \\
\bottomrule
\end{tabular}
\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please. Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens? And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes. This way we'll be able to see differences across domains.}}
\label{tab:rel}
\end{table}

@@

\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.} \gbt{I think it'd be best to put the out-of-wordnet info in the Lexical relations table -- this way we have everything in one place.}

@@

\subsection{Beyond synonymy and hypernymy: cross-classification}

\gbt{@Sina, for this section/my analysis, I'd need csvs (or some code that builds dataframes) containing the following:}

  \begin{enumerate}
  \item Dataframe for images: for each image,
    \begin{itemize}
    \item top -- top name
    \item \% top
    \item SN -- snodgrass agreement
    \item =VG
    \item dictionary or similar with names and counts
    \end{itemize}
  \item Dataframe for name variants: for each variant pair,
    \begin{itemize}
    \item top name
    \item variant
    \item frequency of the pair
    \item domain of top
    \item domain of variant (one of ours or ``OTHER'' if not in any of them?)
    \item relationship in wordnet, one of: synonymy, hyponymy, co-hyponymy, other, not in wordnet (agree? the latter means ``one of the elements not in wordnet'')
    \end{itemize}
  \end{enumerate}

@@

\begin{itemize}
\item lettuce -- salad
\item fruit -- food
\item man -- catcher
\item bowl --chili
\item bowl -- diner \gbt{spelling mistake? should be dinner?} 
\item burger -- meat
\item statue -- animal (image shows statue of an animal)
\item bottle -- alcohol
\item donut --desert \gbt{spelling mistake? should be dessert?} 
\item zebra -- stripes
\item oven -- grill
\end{itemize}

@@

% \subsection{Entry-level names and preference orders....}

% \sz{an interesting example:} In our data set, there are 24 images where \textit{penguin} has been used, so we know that the object is a \textit{penguin}. For 50\% of these images, annotators still prefer \textit{bird} as the most common name. According to the theory of entry-level categories, this should not happen. People should always prefer \textit{penguin} over \textit{bird}.

% \sz{how can we analyze this quantitatively?}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
